Precise predictions for same-sign W-bosons scattering at the LHC

### 2018-01-25 Draft/scanNLO.tex
Update scanNLO.tex

{\bf GP: Comment on the $m_{jj}, \Delta y_{jj}$ distributions, mainly in the region $200 < m_{jj} < 500$ and $2<|\Delta y_{jj}|<2.5$.}
\begin{figure}[hbt]
\centering
{\includegraphics[scale=0.35]{mjj_nlo.pdf}}
{\includegraphics[scale=0.35]{dyjj_nlo.pdf}}
\caption{NLO QCD inclusive study: distributions in $m_{jj}$ (left) and $\Delta y_{jj}$ (right), obtained with full ({\sc Recola}) and approximated ({\sc Vbfnlo, Bonsay}) amplitudes at order $\mathcal{O}(\alpha^6\alpha_s)$.} \label{fig:mjjdyjj_1d_1}
\end{figure}

{\bf GP: Comment on the $m_{jj}, \Delta y_{jj}$ 2D scan: s--channels yes/no, left discrepancies after s--channel inclusion.}
\begin{figure}[h]
\centering
{\includegraphics[scale=0.39]{a6as_vbfnloVSrecola_tu.pdf}} 
%\includegraphics[scale=0.395]{figures/scanfigures/.pdf}
\caption{Cross sections (fb) per bin of $(m_{jj},\,\Delta y_{jj})$ at NLO QCD $\mathcal{O}(\alpha^6\alpha_s)$, without any cut on the $jj$ pair kinematics: ratio of approximated squared amplitudes over the full matrix element. The approximated squared amplitudes are computed as $|\mathcal{A}|^2 \sim |t|^2 + |u|^2$. Results of {\sc Vbfnlo} (approximated) and {\sc Recola} (full) calculations.}\label{fig:ratio2d_NLO}
\end{figure}

\begin{figure}[hbt]
\centering
{\includegraphics[scale=0.39]{a6as_vbfnloVSrecola_stu.pdf}}
\caption{Cross section (fb) per bin of $(m_{jj},\,\Delta y_{jj})$ at NLO QCD $\mathcal{O}(\alpha^6\alpha_s)$, without any cut on the $jj$ pair kinematics:  ratio of approximated squared amplitudes over the full matrix element. The approximated squared amplitudes are computed as $|\mathcal{A}|^2 \sim |s|^2 + |t|^2 + |u|^2$. Results of {\sc Vbfnlo} (approximated) and {\sc Recola} (full) calculations.}\label{fig:mjjdyjj_2d_NLO}
\end{figure}

{\bf GP: Comment on the other distributions: all the plots ?}
\begin{figure}[hbt]
\centering
{\includegraphics[scale=0.35]{ptj1_nlo.pdf}}
{\includegraphics[scale=0.35]{ptj2_nlo.pdf}}
\caption{NLO QCD inclusive study: $p_t$ distributions of the two leading jets, obtained with full ({\sc Recola}) and approximated ({\sc Vbfnlo, Bonsay}) amplitudes at order $\mathcal{O}(\alpha^6\alpha_s)$.} \label{fig:mjjdyjj_1d_2}
\end{figure}

\begin{figure}[hbt]
\centering
\fbox{\includegraphics[scale=0.35]{ptj3_nlo.pdf}}
\fbox{\includegraphics[scale=0.35]{yj1_nlo.pdf}}
\fbox{\includegraphics[scale=0.35]{yj2_nlo.pdf}}
\fbox{\includegraphics[scale=0.35]{mll_nlo.pdf}}
\fbox{\includegraphics[scale=0.35]{zel_nlo.pdf}}
\fbox{\includegraphics[scale=0.35]{zmu_nlo.pdf}}
\caption{{\bf FIGURES STILL TO BE MODIFIED} } \label{fig:mjjdyjj_1d_3}
\end{figure}

>>>>

{\bf GP: Comment on the $m_{jj}, \Delta y_{jj}$ distributions, mainly in the region $200 < m_{jj} < 500$ and $2<|\Delta y_{jj}|<2.5$.}
\begin{figure}[hbt]
\centering
{\includegraphics[scale=0.35]{figures/scanfigures/mjj_nlo.pdf}}
{\includegraphics[scale=0.35]{figures/scanfigures/dyjj_nlo.pdf}}
\caption{NLO QCD inclusive study: distributions in $m_{jj}$ (left) and $\Delta y_{jj}$ (right), obtained with full ({\sc Recola}) and approximated ({\sc Vbfnlo, Bonsay}) amplitudes at order $\mathcal{O}(\alpha^6\alpha_s)$.} \label{fig:mjjdyjj_1d_1}
\end{figure}

{\bf GP: Comment on the $m_{jj}, \Delta y_{jj}$ 2D scan: s--channels yes/no, left discrepancies after s--channel inclusion.}
\begin{figure}[h]
\centering
{\includegraphics[scale=0.39]{figures/scanfigures/a6as_vbfnloVSrecola_tu.pdf}} 
%\includegraphics[scale=0.395]{figures/scanfigures/.pdf}
\caption{Cross sections (fb) per bin of $(m_{jj},\,\Delta y_{jj})$ at NLO QCD $\mathcal{O}(\alpha^6\alpha_s)$, without any cut on the $jj$ pair kinematics: ratio of approximated squared amplitudes over the full matrix element. The approximated squared amplitudes are computed as $|\mathcal{A}|^2 \sim |t|^2 + |u|^2$. Results of {\sc Vbfnlo} (approximated) and {\sc Recola} (full) calculations.}\label{fig:ratio2d_NLO}
\end{figure}

\begin{figure}[hbt]
\centering
{\includegraphics[scale=0.39]{figures/scanfigures/a6as_vbfnloVSrecola_stu.pdf}}
\caption{Cross section (fb) per bin of $(m_{jj},\,\Delta y_{jj})$ at NLO QCD $\mathcal{O}(\alpha^6\alpha_s)$, without any cut on the $jj$ pair kinematics:  ratio of approximated squared amplitudes over the full matrix element. The approximated squared amplitudes are computed as $|\mathcal{A}|^2 \sim |s|^2 + |t|^2 + |u|^2$. Results of {\sc Vbfnlo} (approximated) and {\sc Recola} (full) calculations.}\label{fig:mjjdyjj_2d_NLO}
\end{figure}

{\bf GP: Comment on the other distributions: all the plots ?}
\begin{figure}[hbt]
\centering
{\includegraphics[scale=0.35]{figures/scanfigures/ptj1_nlo.pdf}}
{\includegraphics[scale=0.35]{figures/scanfigures/ptj2_nlo.pdf}}
\caption{NLO QCD inclusive study: $p_t$ distributions of the two leading jets, obtained with full ({\sc Recola}) and approximated ({\sc Vbfnlo, Bonsay}) amplitudes at order $\mathcal{O}(\alpha^6\alpha_s)$.} \label{fig:mjjdyjj_1d_2}
\end{figure}

\begin{figure}[hbt]
\centering
\fbox{\includegraphics[scale=0.35]{figures/scanfigures/ptj3_nlo.pdf}}
\fbox{\includegraphics[scale=0.35]{figures/scanfigures/yj1_nlo.pdf}}
\fbox{\includegraphics[scale=0.35]{figures/scanfigures/yj2_nlo.pdf}}
\fbox{\includegraphics[scale=0.35]{figures/scanfigures/mll_nlo.pdf}}
\fbox{\includegraphics[scale=0.35]{figures/scanfigures/zel_nlo.pdf}}
\fbox{\includegraphics[scale=0.35]{figures/scanfigures/zmu_nlo.pdf}}
\caption{{\bf FIGURES STILL TO BE MODIFIED} } \label{fig:mjjdyjj_1d_3}
\end{figure}
